
\part{Examples}
\chapter{Introduction}
A variety of texts have been translated into Thiguka. The first major complete translation, from mid-April 2024, is Wikipedia's article on Lena Raine, an American music composer from Seattle who has made music for Minecraft.

The translation on Lena Raine is subject to errors, being an early text and not having been updated to reflect the latest changes to the Thiguka language as of May 2024.

\section{Smaller examples}
\ex
\begingl
    \gla \textbf{thi}~\textbf{gu}-\textbf{ka}geta thil//
    \glb \agradj{}-mouth thing//
    \glft `mouth thing'//
\endgl
\xe

\ex
\begingl
    \gla Lahkelakesi-pah fusala laki!//
    \glb make.building-NOM must grow//
    \glft `The factory must grow!'//
\endgl
\xe

\ex
\begingl
    \gla Kalisu pelu pa-gasari-ta?//
    \glb what person PFV-action.V-PST//
    \glft `Who did it?'//
\endgl
\xe

\ex
\begingl
    \gla Kake-pah fusala lahkela lahfisipaka-tay-sa.//
    \glb 2SG-NOM must make conlang-ACC-SG//
    \glft `You must make a conlang.'//
\endgl
\xe

\ex
\begingl
    \gla Ifil ta~gu-li-kala    tayle, pothu-pah gulaya      lifil  Sikago-kala alu pa-bafatha-ta Los Algeles-kala//
    \glb in   AGR~ADJ-NEG-know time   3SG-NOM   COP.3SG.PRS NEG.in Chicago-LOC and PFV-go.to-PST Los Angeles-LOC//
    \glft At some point in time, she moved from Chicago to Los Angeles.\\
          (lit. In an unknown time, she was no longer in Chicago; and she went to Los Angeles.)//
\endgl
\xe

\ex
\begingl
    \gla  thaka-pah isa la~gu-olatha  larakas kake-pafay lahfispaka-tay-sa //
    \glb  1SG-NOM   one AGR~ADJ-month steal.V 2SG-GEN    conlang.ACC-SG //
    \glft I will take away your conlang for a month.\\
          (lit. "I will one-month steal your conlang")//
\endgl
\xe

\ex
\begingl
\gla thaka-pah sa-ri-fathas-a   a\~{}gu-ret   asalisa-tay //
\glb 1SG-NOM   IPFV-INT-see-PRS \agradj{}-red sun-ACC //
\glft ``I stare into the red sun'' //
\endgl
\xe

\ex
\begingl
\gla Asila pasla-pah gulaya      fah\~{}gu-gahlirithi aka~gu-fahparakala-elah akath.
+ Kasa pasla-pah pafay-sa ri\~{}gu-kageta  rifari-tay-elah//
\glb that  place-NOM COP.3SG.PRS \agradj{}-violin    \agradj{}-student-PL      full   this place-NOM has-PRS  \agradj{}-mouth music-ACC-PL//
\glft That room over there is full of violin students, while this room is for vocals. \\
     (lit. "That place is violin-student-full. This place has mouth musicians")//
\endgl
\xe

\ex
\begingl
\gla  o\~{}gu-tubi    fahofefi gulaya      ifil tubipasla-kala//
\glb  \agradj{}-water vehicle  COP.3SG.PRS in   sea-LOC//
\glft The boat is in the sea.//
\endgl
\xe

\ex
\begingl
\gla  Asalisa-pah pa-lahkela-ta layta-tay-elah//
\glb  sun-NOM     PFV-make-PST  light-ACC-PL//
\glft The sun shone. \\
      (lit. "The sun made light.")//
\endgl
\xe

\ex
\begingl 
\gla  Fahkolugeyle-pafay balisa   pa\~{}gu-li-kala     pa-bafatha-ta pothu-tay. Asila efete-pah pa-kufa-ta    pothu-tay talo  sa\~{}gu-iluto   pa-sakara-sa geyle-tay alu pa-kasafay-sa      pothu-pafay  balisa-lay   alu pa-pafay-sa  fula\~{}gu-fusta              fulakari-tay-sa//
\glb  gamer-GEN.POSS     daughter \agradj{}-NEG-known  PFV-go.to-PST 3SG-ACC    that  event-NOM PFV-cause-PST 3SG-ACC   three \agradj{}-minute PFV-stop-PRS game-ACC  and PFV-take\_care-PRS 3SG-GEN.POSS daughter-DAT and PFV-have-PRS \agradj{}-short short\_break-ACC-SG//
\glft The player suddenly had their daughter come up to them so they paused the game for 3 minutes to take care of their daughter and have a short break.//
\endgl
\xe

\textit{fusta} is used for an unspecified length of time from one minute to one day.

\input{parts/examples/lenaraine.tex}

\chapter{Mid-sized translations}
\input{parts/examples/beemovie.tex}
\newpage
\input{parts/examples/funactivities.tex}
\newpage
\input{parts/examples/c418.tex}

\newpage
