\documentclass{thigukabook}
\usepackage{bookmark}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{lmodern}
\usepackage{multicol}

\usepackage{expex}
\lingset{everygla=, belowglpreambleskip=-0.5ex, aboveglftskip=-0.5ex} % gloss formatting

\usepackage[margin=4em]{geometry}

\usepackage{array}
\usepackage{tipa}
\usepackage{textcomp}

\usepackage{fontspec}
    \setmainfont{Gentium Plus}

% Change this filename to the name of whatever you're writing about the language.

% Thiguka is in the public domain; and so is its documentation!


\title{The Thiguka Language}
\date{June 2024}
\author{Lemuria}

\begin{document}

\maketitle

\newpage

\thigukacopyright{}


\section*{About}
Thiguka is a constructed language that Lemuria has continued to develop since April 2024.
This contains a full description of Thiguka's grammar, ready for your reading pleasure.

\section*{Glossing abbreviations}
\agradj is used for adjective agreement.

\ex
\begingl
    \gla  tu\~{}{}gu-elo tubi//
    \glb  AGR\~{}ADJ-yellow water//
    \glft `urine'//
\endgl
\xe

PROX is used for the proximal determiner.

MED is used for the medial determiner.

DIS is used for the distal determiner.

\section*{Acknowledgements}
Thank you for reading the Thiguka documentation.

There are some people who have (constructively) criticized Thiguka; the criticism I want and need to make Thiguka a better and more well-documented language.

So far the only person to offer any extensive criticism is Zethar of the Conlangs Discord Network; in June 2024, I took part in a translation relay that Zethar hosted.
At the end of the contest I received about a page's worth of criticism, which I used to further improve Thiguka's documentation.

\tableofcontents

\part{Language}

\include{parts/phonology}
\include{parts/grammar}
\include{parts/orthography}
\include{parts/lexicon}
\include{parts/syntax}
\include{parts/examples}

\end{document}
