\newpage

\subsection{Bee Movie script}

\subsubsection*{English}
According to all known laws of aviation, there is no way a bee should be able to fly.
Its wings are too small to get its fat little body off the ground.
The bee, of course, flies anyway because bees don't care what humans think is impossible.

\subsubsection*{Thiguka}
Lafad fagulufah lugufahofefi tharasagpahelah fiasaga bigulufahta bitaysa.
Pothupafay lirukpahelah parilitisi suf ofefi dogufalatha dogurilitisi doros okulusat gawralay.
Bipahsa lufahta alu likolaga pelupafayelah udiltayelah las asaga.

\subsubsection*{Gloss}
\begin{exe}
    \ex{} \gll{}Lafad fa~gu-lufah lu~gu-fahofefi tharasag-pah-elah fi-asaga bi~gu-lufah-ta bi-tay-sa.\\
                all AGR~ADJ-air AGR~ADJ-vehicle law-NOM-PL NEG-allow AGR~ADJ-fly-PRS bee-ACC-SG.\\
          \glt{}All airplane laws do not allow flying bees.
\end{exe}

\begin{exe}
    \ex{} \gll{}Pothu-pafay liruk-pah-elah  pari-litisi suf ofefi  do~gu-falatha do~gu-rilitisi doros okulusat gawralay.\\
                3SG-POS wing-NOM-PL  excessive.INT-small to move  AGR~ADJ-fat AGR~ADJ-little body off ground\\
          \glt{}Its wings are too small to move a fat little body off the ground.
\end{exe}

\begin{exe}
    \ex{} \gll{}Bi-pah-sa lufah-ta alu li-kolaga pelu-pafay-elah udil-tay-elah las asaga.\\
                Bee fly.V-PRS and NEG-comply person-GEN-PL think-ACC-PL COP allow.ADJ\\
          \glt{}Bees fly and do not comply with people's thoughts of what is allowed.
\end{exe}


