

\chapter{C418}
To finish off all the Minecraft composers, here's C418.

\section{Thiguka}
Deylijel Roselfeldpah (berethata 1989-05-09), leylesathasi C418, gulaya tagu-Duylslald tarifari ifil kolugeyle Maylakraflay.
Pothu-tay pakalasa dasili pothupah gulaya fahguifiltatayle fahlahpeyrifaritaysa alu fahguritu fahlahkela ifil kolugeyle Maylakrafkala.
Pothu-pah pafay Deifi Redele-pafay alu Karla Sibolapafay talit, palahkelata gigulahkelakolugeyle giled Aifi Rod-tay.

Pothupah ferayfatathasi alu felahkelatathasi rifaritaysa Biold Stereysere Thillayelah alu Kuki Klikere-pafay fagu-Sti fathusilaysa.
Pothupah fediseytathasi Alabalagusi-lay, si gulaya rigu-Arika rigusutefari rifalagiled.

\subsection{Siguaga sifata}
Roselfeld-pah gulata paberethata ifil duguisefe Duylslald-kala ifil 1989-05-09.
Roselfeld-pah gulaya begu-Sofijet tagupaberethata alu taligu-Duylslald tagulitasafa alu tagufahlahgulelothi talipafay alu lagu-Duylslald laysapafay batoli.

Pothupah paparakalata gesalahrifaritay skiguaga Skisi Trakere-kithi, si gulaya klogu-Ilpuls Trakere klole, alu Eybeltolo Laif ifil tuguaga 2000-elah.
Rafupah poguta thigufikafahra thilgula ifil asila taylekala.
Pothu-pafay ibatoli, Ari Roselfeld-pah (Ilgis: Harry Rosenfeld) fathusi gesalahrifaritay pothulay Ilpuls Trakere-kithi.
Aripah pasipikta ``likalapeluifele'' (Ilgis: ``even an idiot'') lahgugulid lahkela rifari-tay pothukithi.
Pothupafay ibatoli, leylesathasi C818.
Asilapah pakufata pothutay pafay leyle C418, si gesipiksa asila leylepah gulaya lipafay sipithikala.

\newpage

\section{Gloss}

\ex
\begingl
          \gla  Deylijel Roselfeld-pah (beretha-ta 1989-05-09), leyle-sa=thasi C418,//
          \glb  Daniel Rosenfeld-NOM (born-PST 1989-05-09) name-PRS=also C418.PR//
          \glft Daniel Rosenfeld (born May 9, 1989) also named C418,//
\endgl
\xe

\ex
\begingl
          \gla  gulaya ta\~{}gu-Duylslald tarifari ifil kolugeyle Maylakraf-lay.//
          \glb  COP.3SG.PRS AGR\~{}ADJ-Germany musician in video.game Minecraft-DAT//
          \glft is a German musician in the video game Minecraft.//
\endgl
\xe

\ex
\begingl
          \gla  Pothu-tay pa-kala-sa dasili pothu-pah gulaya fah\~{}gu-ifil-tatayle fahlahpeyrifaritay-sa alu fah\~{}gu-ritu fah-lahkela ifil kolugeyle Maylakraf-kala//
          \glb  3SG-NOM PFV-know-PST because 3SG-NOM COP.3SG.PRS AGR\~{}ADJ-in-past composer-ACC-SG and AGR\~{}ADJ-sound AGT-make in video.game Minecraft-LOC//
          \glft He is known because he is the past composer and sound maker in the video game Minecraft.//
\endgl
\xe

\ex
\begingl
          \gla  Pothu-pah pafay Deifi Redele-pafay alu Karla Sibola-pafay talit, pa-lahkela-ta gi\~{}gu-lahkela-kolugeyle giled Aifi Rod-tay, si gulaya ge-lahkela-sa kolugeyle Alderstop-tay//
          \glb  3SG-NOM with Davey Wreden-GEN and Karla Zimonja-GEN help, PFV-make-PST AGR\~{}ADJ-make-video.game group Ivy Road.PR-ACC REL COP.3SG.PRS PROG-make-PRS video.game Wanderstop-ACC//
          \glft He, with Davey Wreden and Karla Zimonja's help, made the video game development organization Ivy Road, which is making Wanderstop.//
\endgl
\xe

\ex
\begingl
          \gla  Pothu-pah fe-rayfa-ta=thasi   alu fe-lahkela-ta=thasi rifari-tay-sa  Biold   Stereysere Thil-lay-elah alu Kuki   Klikere-pafay fa\~{}gu-Sti     fathusi-lay-sa  //
          \glb  3SG-NOM   PERF-write-PST=also and PERF-make-PST=also  music-ACC-SG   Beyond  Stranger   Thing-DAT-PL  and Cookie Clicker-GEN   AGR\~{}ADJ-Steam release-DAT-SG //
          \glft He has written also and made also music for Beyond Stranger Things, and Cookie Clicker's Steam release.//
\endgl
\xe

\ex
\begingl
          \gla  Pothu-pah fe-disey-ta=thasi Alabalagusi-lay, si  gulaya      ri\~{}gu-Arika     ri\~{}gu-sutefari     rifalagiled//
          \glb  3SG-NOM   PERF-dj-PST=also  Anamanaguchi-DAT REL COP.3SG.PRS AGR\~{}ADJ-America AGR\~{}ADJ-rock.music band//
          \glft He has DJed also for Anamanaguchi, which is an American rock band.//
\endgl
\xe

\newpage

\subsection{Early life / Siguaga sifata}
\ex
\begingl
\gla  Roselfeld-pah gulata      pa-beretha-ta ifil du\~{}gu-isefe Duylslald-kala ifil 1989-05-09.//
\glb  Rosenfeld-NOM COP.3SG.PST PFV-birth-PST  in   \agradj{}-east Germany-LOC    in   1985-05-09//
\glft Rosenfeld was born in East Germany on 1989-05-09,//
\endgl
\xe

\ex
\begingl
\gla  Roselfeld-pah gulaya      be\~{}gu-Sofijet ta\~{}gu-pa-beretha-ta alu tali\~{}gu-Duylslald ta\~{}gu-litasafa alu ta\~{}gu-fahlah-gulelothi tali-pafay      alu //
\glb  Rosenfeld-NOM COP.3SG.PST \agradj{}-Soviet \agradj{}-PFV-birth-PST and \agradj{}-Germany   \agradj{}-descent and \agradj{}-maker-gold      father-GEN.POSS and //
\glft Rosenfeld is a Soviet-born and German-descent and goldsmith father's and//
\endgl 
\xe


Descent was translated as \textit{litasafa}, the opposite of \textit{tasa} (``high, to go up, up'').

\ex
\begingl
\gla  la\~{}gu-Duylslald laysa-pafay batoli//
\glb  \agradj{}-Germany  mother-GEN.POSS son//
\glft German mother's son.//
\endgl
\xe

\ex
\begingl
\gla  Pothu-pah pa-parakala-ta gesa-lah-rifari-tay   ski\~{}gu-aga   skisi  trakere-kithi, si  gulaya      klo\~{}gu-Ilpuls  Trakere klole//
\glb  3SG-NOM   PFV-learn-PST  act.of-make-music-ACC \agradj{}-early Schism Tracker-INS,   REL COP.3SG.PRS \agradj{}-Impulse Tracker clone//
\glft He learned musicmaking with early Schism Tracker, which is an Impulse Tracker clone//
\endgl
\xe

\ex
\begingl
\gla  alu Eybeltolo Laif ifil tu\~{}gu-aga    2000-elah.//
\glb  and Ableton   Live in   \agradj{}-early 2000-PL//
\glft and Ableton Live, in the early 2000s.//
\endgl
\xe

\ex
\begingl
\gla  rafu-pah poguta      thi\~{}gu-fikafahra   thil-gula ifil asila tayle-kala//
\glb  3PL-NOM  COP.3DU.PST \agradj{}-rudimentary thing-DU  in   that  time-LOC//
\glft They were both rudimentary things in that time.//
\endgl
\xe

\ex
\begingl
\gla  Pothu-pafay  ibatoli, Ari   Roselfeld-pah, fathusi gesa-lah-rifari-tay   pothu-lay Ilpuls  Trakere-kithi//
\glb  3SG-GEN.POSS brother  Harry Rosenfeld-NOM  expose  act.of-make-music-ACC 3SG-DAT   Impulse Tracker-INS//
\glft It was his brother, Harry Rosenfeld, who introduced him to music composition through Impulse Tracker.//
\endgl
\xe

\ex
\begingl
\gla  Ari-pah   pa-sipik-ta   ``likalapelu=ifele'' lah\~{}gu-gulid    lahkela rifari-tay pothukithi.//
\glb  Harry-NOM PFV-speak-PST ``dumb.person=even`` \agradj{}-good.ADV make    music-ACC  3SG-INS//
\glft Harry said "even an idiot" can goodly create music with it.//
\endgl
\xe

"idiot" was translated as \textit{likalapelu} - "dumb person", lit. "not-knowledge person".

His brother was also known as C818, from which he chose the name C418, claiming that the name is "really cryptic and doesn't actually mean anything."

\ex
\begingl
\gla  Pothu-pafay  ibatoli, leyle-sa=thasi C818.//
\glb  3SG-GEN.POSS brother  name-PRS=also  C818.//
\glft His brother was also named C818.//
\endgl
\xe

\ex
\begingl
\gla  Asila-pah pa-kufa-ta   pothu-tay pafay leyle C418, si  ge-sipik-sa    asila leyle-pah gulaya      li-pafay sipithi-kala.//
\glb  that-NOM  PFV-make-PST 3SG-ACC   have  name  C418, REL PROG-speak-PRS that  name-NOM  COP.3SG.PRS NEG-have word-knowledge.//
\glft That made him have the name C418, saying that name is "really cryptic and has no meaning."//
\endgl
\xe

\section{English original (Wikipedia)}
Daniel Rosenfeld (born 9 May 1989), better known as C418 (pronounced "see four eighteen"),[4] is a German musician, producer and sound engineer.
He is best known as the former composer and sound designer for the sandbox video game Minecraft.
He is a co-founder of independent video game developer Ivy Road with Davey Wreden and Karla Zimonja, which is developing Wanderstop. 

He has also written and produced the theme for Beyond Stranger Things and the Steam release of Cookie Clicker.
He has also DJed for American rock band Anamanaguchi. 

\subsection{Early life}
Rosenfeld was born in East Germany on 9 May 1989, the son of a Soviet-born father of German descent working as a goldsmith and a German mother.
He learned to create music on early versions of Schism Tracker (a popular clone of Impulse Tracker) and Ableton Live in the early 2000s, both rudimentary tools at the time.
It was his brother, Harry Rosenfeld, who introduced him to music composition through Impulse Tracker, commenting that "even an idiot" can successfully create music with it.
His brother was also known as C818, from which he chose the name C418, claiming that the name is "really cryptic and doesn't actually mean anything."
% Rosenfeld has also stated that he was "mediocre at school," but learning basic music theory and English came easy to him.

\section{English literal}
Daniel Rosenfeld (born May 9, 1989) also named C418, is a German musician in the video game Minecraft.
He is known because he is the past composer and sound maker in the video game Minecraft.
He, with Davey Wreden and Karla Zimonja's help, made the video game development organization Ivy Road.

He has written also and made also music for Beyond Stranger Things, and Cookie Clicker's Steam release.
He has DJed also for Anamanaguchi, which is an American rock band.

\subsection{Early life}
Rosenfeld was born in East Germany on 1989-05-09.
Rosenfeld is a Soviet-born and German-descent and goldsmith father's and German mother's son.
He learned musicmaking with early Schism Tracker, which is an Impulse Tracker clone, and Ableton Live, in the early 2000s.
They were both rudimentary things in that time.
It was his brother, Harry Rosenfeld, who introduced him to music composition through Impulse Tracker.
Harry commented that "even an idiot" can goodly create music with it.
His brother was also named C818.
That made him have the name C418, saying that name is "really cryptic and has no meaning."
