
\section{Fun activities}
This was the sample passage for Conlang Ambassadors 3, a translation activity from May--June 2024.
\subsection*{English}
There are many forms of fun activities in general.
For example, there are hobbies which such as hiking, collecting themed objects, or non-professional creative arts and crafts.
Some people like to play games or sports, or just like to enjoy looking at people's pictures, listen to other people's music, or watch other people perform.
So long as someone enjoys the activity it is a reasonable recreational pastime.

\subsection*{Thiguka}
Elah lisure saparapahelah esahlasa.
Fulafatasa, pafaysa thigusapara thilelah, alu aragulisaleyfata arafat lores lisugufuros lilahkela ligupera lisure.
Pelupah falusaya geyletayelah, gasari isi fathasa lipothu pelupafay kurakatayelah, rififeyla lipothu pelutayelah, fathas pegulipothu pegusiligara pelutayelah, fathas pegulipothu pegusiligara pelutayelah.
Kula pelupah falusaya lisuretay, pothu gulaya ligurigulid lisure.

\subsection*{Gloss}
\ex
\begingl
\gla Elah lisure sapara-pah-elah esahlasa.//
\glb many fun.activity kind-NOM-PL exist.V-PRS//
\glft `Many fun activity types exist.'//
\endgl
\xe

\ex
\begingl
\gla  Fulafata-sa, pafay-sa thi\~{}gu-sapara thil-elah, alu ara\~{}gu-li-saleyfata arafat-elah alu fulahthi lores lisu\~{}gu-furos li-lahkela li\~{}gu-pera lisure.//
\glb  hike-PRS, have-PRS \agradj-type thing-PL, and \agradj-NEG-occupation art-PL and fun.make.thing-PL COP.3PL.PRS \agradj-fun NEG-make \agradj-money fun.activity.//
\glft `Hiking, having themed objects, and non-professional art are fun not-money-making hobbies.'//
\endgl
\xe

\ex
\begingl
\gla  Pelu-pah falusaya geyle-tay-elah, gasari isi fatha-sa pe\~{}gu-li-pothu pelu-pafay kuraka-tay-elah, rififeyla li-pothu pelu-tay-elah, fathas pe\~{}gu-li-pothu pe\~{}gu-siligara pelu-tay-elah.//
\glb   person-NOM like game-ACC-PL, action of see.V-PRS \agradj-NEG-3SG person-GEN image-ACC-PL, listen.to.music NEG-3SG person-ACC-PL, see.V \agradj-NEG-3SG \agradj-perform person-ACC-PL.//
\glft `An unspecified amount of people like games, the act of seeing others' pictures, listening to others' music, or watching performing people.'//
\endgl
\xe

\ex
\begingl
    \gla Kula pelu-pah   falusaya lisure-tay,       pothu gulaya      li\~{}gu-ri-gulid   lisure.//
    \glb If   person-NOM enjoy    fun.activity-ACC, it    COP.3SG.PRS \agradj-INT-good fun.activity.//
    \glft `If a person enjoys a fun activity, it is a good fun activity.'//
\endgl
\xe

