\chapter{Lena Raine}
This article on Lena Raine comes from Wikipedia. Wikipedia's content is licensed under CC BY-SA 4.0; the text of this license is at \url{https://en.wikipedia.org/wiki/Wikipedia:Text_of_the_Creative_Commons_Attribution-ShareAlike_4.0_International_License}. A verbatim copy of the original English article text is included here for easier comparison.

\section{Translation notes}
As Lemuria works on Thiguka, his knowledge of linguistics grows ever-larger.
Here is a translation of the first sentence of Wikipedia's article on Lena Raine, in two versions; the old version from April 2024 and the new one from June 2024.

\section{Thiguka}
Lela Reyl (Ilgis: Lena Raine; berethata 1984-02-29), leylesathasi Lela Sapel (Ilgis: Lena Chappelle) aluthasi Kureyl (Ilgis: Kuraine) gulaya Taguarika alu Tagukalada tagulikageta tarifari alu lisapahsa lahkelasa kolugeyletayelah.
Pelupahelah kalasa Reyltay pur pothupafay leyguritu leyboro ifil Selesete alu Maylakraf alu kigugiled kisufetelah dalata.
Pothupah lahkelasathasi rifaritay ifil kolugeyletayelah sufadhas Deletarule alu Sikori: Sigukothor Sifothisa. 

\subsection{Siguaga sifata}
Reylpah berethata 1984-02-29 ifil Siatel ifil Asiltol.
Pothupafay tali tarifari alu pothupafay laysa pelifefi.
Fipothupafay tagukuyri tarifagetata alu pothupah fathusita pothutay ifil tarifari.
Pothupafay tali-thasi fahgahlirithi.
Solik Edeog sigupeke pegusifothi peli giledsa fathusita pothutay ifil pagulidi patefarielah.
Reylpah pagulidi patefarikithielah taguisasafi lahkeluta rifaritayelah pothu kalata aludhete lahkelata pothupafay tagubage tarifari.
Teroti kuthifa, pothupah kalata ifil Kornis ogukala ose Arafatelah.
Teroti kuthifa, Kornispah salathta Reyltay lahgurifari lahkelasa oselufasa.

\subsection{Sifutila}
Pelupahelah kalasa Reyltay pur pothupafay leyguritu leyboro ifil Selesete alu Kigugiled Kisufetelah Dalata. 
Pothupah leyborota ifil Kigugiled Kisufetelah Dalata ArilaLetkala pur fagugati fasatelah gafalu fahpaterelahkesa alu fahlahkelapahsa ritutay.

Pothupah alu Lakleyl Diler, gafalu oguifil ose fahlahkelapahgula ritutay ifil geylepafay lisufasa ifil 2015, Kigugiled Kisufetelah Dalata: Arfaspafaysa Thigusapagad Thilelah.
Pothupah falgathata ArilaLetay ifil 2016, bulu pogufilasar pothupah lahkelata rifaritayelah ifil ArilaLetpafay kolugeylelah.

Ifil 2018, Reylpah fathusita afegurayfathil koguafeltur kolugeyle esektay ifil itisayokala.
Reylpah lahkelata rifaritay alu lahkelata kolugeyletay esektay alu Deytaireyspah (Ilgis: Dataerase) lahkelata arafatayelah.
Ifil 2019, pothupah fathusita riguisasafi rifari, Isakalasa.

Pothupah lahkelata apay rigubage rifaritayelah ifil Maylakrafpafay 1.16 "Lether Patifekalasa" (Ilgis: Nether Update) ifil 2020.
Faguisa fasatefay, pothupah alu tagukolugeyle tarifarisa Kuli Taliokapah lahkelata gati rigubage rifaritayelah ifil 1.18 "Kelefitelah alu Sahlagelah: Pagudalatafasi Parafsa" patifekalasa, Faguisa fasatefay, pothupah lahkelata talo rigubage rifaritayelah ifil 1.19 "Pagufaylata Parafsa".

Reylpah lahkelata rifaritay ifil araguafeltur koguarapigi kolugeylekala Sikori: Sigukothor Sifothisa alu tulorta pelutayelah lahkelata rifaritayelah ifil sagudalatafasi sagdathasa ifil Deletarunekala.
Kolugeylepahgula fathusita ifil 2021.

\ex
\begingl
\gla Ifil 2024-05-28, Reyle-pah pa-fathusi-ta      kolugeyle  Alotherili-pafay esahla    kala-tay-sa.//
\glb  on   2024-05-28, Raine-NOM PFV-distribute-PST video.game Anothereal-GEN   existence knowledge-ACC-SG.//
\glft On May 28, 2024, Raine distributed knowledge of Anothereal's existence.//
\endgl
\xe

\ex
\begingl
\gla Alotherili-pah pafay ko\~{}gu-sutebup-tay       alu ko\~{}gu-tugasa     thi\~{}gu-kolugeyle   thil-tay-elah.//
\glb Anothereal-NOM has   AGR\~{}ADJ-shoot.em.up-ACC and AGR\~{}ADJ-roleplay AGR\~{}ADJ-video.game thing-ACC-PL//
\glft Anothereal has shoot 'em up and roleplay game things.//
\endgl
\xe

\subsection{Sigupelu sifata}
Reyguteraseleter Reylpahthasi rayfata agladtaysa, Siti of Taygers aluthasi rayfasa siguelegibiti sigupeke sifothi ifil pothupafay taygurifeyla tayle.

\subsection{Thiguolota thilelah}
Asagata Reyltay pur ologubafata thiguolota thilsa aluthasi pothupafay rifari ifil Selesete risifta Giguarika Giledpafay Tarifarielah, pelupahelah rayfasa agladtayelah alu pelupahelah fathusisa thiltayelah rigulid\\ rigukolugeyle rifari ifil fasate thiguolota thilsa ifil 2019.
Pothupafay rifari ifil Selesetepahthasi risifta rigurigulid asagurifari asagasa ifil thigukolugeyle thiguolota thilelah ifil 2018.

\subsubsection*{April 2024}

\ex
\begingl
\gla Lela Reyl   (beretha-ta 1984-02-29),   leyle-sa-thasi Lela Sapel      alu-thasi Kureyl gulaya       Ta\~{}gu-arika     alu Ta\~{}gu-kalada   ta\~{}gu-li-kageta   tarifari alu lah\~{}gu-lisa   fah-lahkela-pah kolugeyle-tay-elah.//
\glb Lena Raine  (born.V-PST 1984-02-29)    name-PST-also  Lena Chappelle  and-also  Kuraine COP.3SG.PRS AGR\~{}ADJ-America and AGR\~{}ADJ-Canada AGR\~{}ADJ-NEG-mouth musician and AGR\~{}ADJ-woman AGT-make-NOM    video.game-ACC-PL.//
\glft Lena Raine  (born Februrary 29, 1984), also known as Lena Chappelle and Kuraine, is an American and Canadian instrumental musician and woman making video games.//
\endgl
\xe

\newpage

\subsubsection*{June 2024}

\ex
\begingl
\gla Lela Reyl  (beretha-ta 1984-02-29), pafay-sa=thasi leyle Lela Sapel     o  Kureyl, gulaya      fah\~{}gu-Arika    alu fah\~{}gu-Kalada  fahlahpeyrifari-tay-sa alu fah\~{}gu-kolugeyle   fah-lahkela.//
\glb Lena Raine (born.V-PST 1984-02-29), have-PRS=also  name  Lena Chappelle or Kuraine COP.3SG.PRS AGR\~{}ADJ-America and AGR\~{}ADJ-Canada composer-ACC-SG        and AGR\~{}ADJ-video.game AGT-make//
\glft Lena Raine (born February 29, 1984), who has also the name Lena Chappelle or Kuraine, is an \\American and Canadian composer, and video game maker.//
\endgl
\xe

\section{Gloss}

\ex
\begingl
\gla  Lela Reyl (beretha-ta 1984-02-29), pafay-sa=thasi leyle Lela Sapel o Kureyl, gulaya fah~gu-Arika alu fah~gu-Kalada fahlahpeyrifari-tay-sa alu fah~gu-kolugeyle fah-lahkela.//
\glb  Lena Raine (born.V-PST 1984-02-29), have-PRS=also name Lena Chappelle or Kuraine COP.3SG.PRS AGR~ADJ-America and AGR~ADJ-Canada composer-ACC-SG and AGR~ADJ-video.game AGT-make//
\glft Lena Raine (born February 29, 1984), who has also the name Lena Chappelle or Kuraine, is an American and Canadian composer, and video game maker.//
\endgl 
\xe

\ex
\begingl 
\gla  Pelu-pah-elah kala-sa Reyl-tay pur pothu-pafay ley~gu-ritu leyboro ifil Selesete alu Maylakraf alu ki~gu-giled kisufete-lah dalata.//
\glb  Person-NOM-PL know-PRS Raine-ACC for 3SG-GEN AGR~ADJ-sound work in Celeste and Minecraft and AGR~ADJ-guild war-PL two.//
\glft People know Raine for her soundtrack work in Celeste, {} Minecraft, and Guild Wars 2.//
\endgl 
\xe

\ex
\begingl
\gla  Pothu-pah lahkela-sa-thasi rifari-tay-elah ifil kolugeyle-tay-elah sufadhas Deletarule alu Sikori: Si~gu-kothor Sifothi-sa.//
\glb  3SG-NOM make-PST-also music-ACC-PL in video game-ACC-PL such as Deltarune and Chicory: AGR~ADJ-color tale-SG//
\glft She has also made music for other video games such as Deltarune and Chicory: A Colorful Tale.//
\endgl 
\xe

\subsection{Early life / Siguaga sifata}

\ex
\begingl
\gla  Reyl-pah beretha-ta  1984-02-29  Siatel-kala Asiltol-kala.//
\glb  Raine-NOM born-PST    Seattle-LOC  Washington-LOC.//
\glft Raine was born on February 29, 1984 in Seattle, Washington.//
\endgl
\xe

\ex
\begingl
\gla  Pothu-pafay tali  tarifari alu pothu-pafay laysa  pelifefi.//
\glb  3SG:N-POS father musician and 3SG:N-POS mother dancer.//
\glft Her father is a musician and her mother is a dancer.//
\endgl
\xe

\ex
\begingl
\gla  Fi-pothu-pafay ta~gu-kuyri tarifageta-ta alu pothu-pah fathusi-ta pothu-tay ifil tarifari.//
\glb  DIM-3SG:N-POS AGR~ADJ-choir sing-PST and 3SG-NOM exposed 3SG-ACC in music.//
\glft Younger-her, in a choir, sang and that exposed her to music.//
\endgl
\xe

\ex
\begingl
\gla  Pothu-pafay tali-thasi  fah-gahlirithi.//
\glb  Her-POS father-also AGT-violin.//
\glft Her father-also was a violinist.//
\endgl
\xe

\ex
\begingl
\gla  Solik Edeog si~gu-peke pe~gu-sifothi peli giled-sa fathusi-ta pothu-tay ifil pa~gu-lidi patefari-elah.//
\glb  Sonic the Hedgehog AGR~ADJ-fictional AGR~ADJ-story-PL community-NOM-SG expose-PST 3SG-ACC in AGR~ADJ-midi arrangement-PL.//
\glft A Sonic the Hedgehog fan community exposed her to MIDI arrangements.//
\endgl
\xe

\ex
\begingl
\gla  Reyl-pah pa~gu-lidi patefari-kithi-elah ta~gu-isa-safi lahkelu-ta rifari-tay-elah pothu kala-ta alu-dhete lahkela-ta pothu-pafay ta~gu-bage tarifari.//
\glb  Raine-NOM AGR~ADJ-midi arrangement-INS-PL AGR~ADJ-one-ORD remake-PST song-ACC-PL 3SG know-PST and-then make-PST 3SG-POS AGR~ADJ-new music.//
\glft Raine, using MIDI arrangements, first recreated songs she knew and then made her own original music.//
\endgl
\xe

\ex
\begingl
\gla  Teroti kuthifa,  pothu-pah kala-ta  Kornis o~gu-kala ose-kala  Arafat-elah.//
\glb  after  long.time 3SG-NOM study-PST Cornish AGR~ADJ-knowledge house-LOC Art-PL.//
\glft Later, she studied in Cornish College of the Arts.//
\endgl
\xe

\ex
\begingl
\gla  Teroti kuthifa,  Kornis-pah salath-ta Reyl-tay  lah~gu-rifari lahkela-sa oselufa-sa.//
\glb  after  long.time Cornish-NOM give-PST Raine-NOM  AGR~ADJ-music make-PST degree-SG//
\glft Later, Cornish gave Raine a music composition degree.//
\endgl
\xe

\subsection{Career}
\ex
\begingl
\gla Pelu-pah-elah kala-sa Reyl-tay pur pothu-pafay ley~gu-ritu leyboro ifil Selesete alu Ki~gu-giled Kisufete-lah Dalata. //
\glb person-NOM-PL know-PRS Raine-ACC for 3SG-POS AGR~ADJ-sound work in Celeste and AGR~ADJ-guild war-PL two. //
\glft People know Raine for her soundtrack work in Celeste and Guild Wars 2. //
\endgl
\xe

\ex
\begingl
\gla Pothu-pah leyboro-ta ifil Ki~gu-giled Kisufete-lah Dalata  ArilaLet-kala pur fa~gu-gati fasate-lah gafalu  fah-paterelahke-sa alu fah-lahkela-pah-sa  ritu-tay. //
\glb 3SG-NOM work-PST in AGR~ADJ-guild war-PL two  ArenaNet-LOC for AGR~ADJ-six year-PL as  AGT-design-SG and AGT-make-NOM-SG  sound-ACC. //
\glft She worked on Guild Wars 2 at ArenaNet for six years as a designer and composer of soundtracks. //
\endgl
\xe

\ex
\begingl
\gla Pothu-pah alu Lakleyl Diler, gafalu o~gu-ifil ose fah-lahkela-pah-gula  ritu-tay ifil  geyle-pafay lisufa-sa ifil 2015, Ki~gu-giled Kisufete-lah Dalata: Arfas-pafay-sa  Thi~gu-sapagad Thil-elah. //
\glb 3SG-NOM and Maclaine Diemer, as AGR~ADJ-in house AGT~make-NOM-DU  sound-ACC in  game-POS expand-SG in 2015, AGR~ADJ-guild war-PL two: heart-POS-SG  AGR~ADJ-sharp thing-PL. //
\glft She and Maclaine Diemer, as in-house composers of soundtracks in the game's expansion in 2015, Guild Wars 2: Heart of Thorns. //
\endgl
\xe

\ex
\begingl
\gla Pothu-pah falgathata ArilaLet-ay ifil 2016, bulu po~gu-filasar pothu-pah lahkela-ta rifari-tay-elah ifil ArilaLet-pafay   kolugeyle-lah. //
\glb 3SG-NOM leave-PST ArenaNet-ACC in 2016, but AGR~ADJ-freelance 3SG-NOM make-PST music-ACC-PL in ArenaNet-POS  video game-PL //
\glft She left ArenaNet in 2016, but freelance her made songs for ArenaNet's other video games. //
\endgl
\xe

\ex
\begingl
\gla Ifil 2018, Reyl-pah fathusi-ta  afe~gu-rayfathil ko~gu-afeltur kolugeyle esek-tay ifil itisayo-kala. //
\glb In 2018, Raine-NOM release-PST  AGR~ADJ-written.thing AGR~ADJ-adventure game ESC-ACC in itch.io-LOC. //
\glft In 2018, Raine released the text adventure video game ESC on itch.io. //
\endgl
\xe

\ex
\begingl
\gla Reyl-pah lahkela-ta rifari-tay alu lahkela-ta kolugeyle-tay esek-tay alu Deytaireys-pah lahkela-ta arafat-ay-elah. //
\glb Raine-NOM make-PST music-ACC and make-PST video game-ACC ESC-ACC and Dataerase-NOM make-PST art-ACC. //
\glft Raine composed and developed ESC and Dataerase made visuals. //
\endgl
\xe

\ex
\begingl
\gla Ifil 2019, pothu-pah fathusi-ta  ri~gu-isa-safi rifari, Isa-kala-sa. //
\glb In 2019, 3SG-NOM release-PST  AGR~ADJ-one-ORD music, one-know-PST. //
\glft In 2019, she released her first album, Oneknowing. //
\endgl
\xe

\ex
\begingl
\gla Pothu-pah lahkela-ta apay ri~gu-bage rifari-tay-elah ifil Maylakraf-pafay 1.16 "Lether Patife-kala-sa" ifil 2020. //
\glb 3SG-NOM make-PST four AGR~ADJ-new music-ACC-PL in Minecraft-POS 1.16 "Nether change-LOC-SG" in 2020. //
\glft She composed four new songs for Minecraft's 1.16 "Nether Update" in 2020. //
\endgl
\xe

\ex
\begingl
\gla Fa~gu-isa fasate-fay, pothu-pah alu  ta~gu-kolugeyle tarifari-sa Kuli Talioka-pah lahkela-ta gati ri~gu-bage rifari-tay-elah ifil 1.18 "Kelefitelah alu Sahlagelah: Pa~gu-dalata-fasi Paraf-sa" patife-kala-sa, //
\glb AGR~ADJ-one year-after.ADV, 3SG-NOM and  AGR~ADJ-video game composer-SG Kumi Tanioka-NOM make-PST six AGR~ADJ-new music-ACC-PL in 1.18 cave-PL and cliff-PL AGR~ADJ-two-ORD part-SG" change-LOC-SG. //
\glft After one year, she and fellow video game composer Kumi Tanioka  made six new songs for 1.18 "Caves and Cliffs: Second Part" update. //
\endgl
\xe

\ex
\begingl
\gla Fa~gu-isa fasate-fay, pothu-pah lahkela-ta talo ri~gu-bage rifari-tay-elah ifil 1.19 "Pa~gu-faylata Paraf-sa". //
\glb AGR~ADJ-one year-after.ADV, 3SG-NOM make-PST three AGR~ADJ-new music-ACC-PL for 1.19 AGR~ADJ-wild change-SG. //
\glft After one year, Raine made three new songs for 1.19 "Wild Update". //
\endgl
\xe

\ex
\begingl
\gla Reyl-pah lahkela-ta rifari-tay ifil ara~gu-afeltur ko~gu-arapigi kolugeyle-kala Sikori: Si~gu-kothor Sifothi-sa alu tulor-ta pelu-tay-elah lahkela-ta rifari-tay-elah ifil sa~gu-dalata-fasi sagdatha-sa ifil Deletarune-kala. //
\glb Raine make-ACC music for AGR~ADJ-adventure AGR~ADJ-rpg video game-LOC Chicory: AGR~ADJ-color tale-SG and assist-PST person-ACC-PL make-PST music-ACC-PL in AGR~ADJ-two-ORD chapter-SG ifil Deltarune-LOC. //
\glft Raine created music for adventure RPG game Chicory: Colorful Tale and assisted people making music in second chapter of Deltarune. //
\endgl
\xe

\ex
\begingl
\gla Kolugeyle-pah-gula fathusi-ta ifil 2021. //
\glb video game-NOM-DU release-PST in 2021. //
\glft Both games released in 2021. //
\endgl
\xe

\ex
\begingl
\gla Ifil 2024-05-28, Reyle-pah pa-fathusi-ta kolugeyle Alotherili-pafay esahla kala-tay-sa. //
\glb on 2024-05-28, Raine-NOM PFV-distribute-PST video.game Anothereal-GEN existence knowledge-ACC-SG. //
\glft On May 28, 2024, Raine distributed knowledge of Anothereal's existence. //
\endgl
\xe

\ex
\begingl
\gla Alotherili-pah pafay ko~gu-sutebup-tay alu ko~gu-tugasa thi~gu-kolugeyle thil-tay-elah. //
\glb Anothereal-NOM has AGR~ADJ-shoot.em.up-ACC and AGR~ADJ-roleplay AGR~ADJ-video.game thing-ACC-PL. //
\glft Anothereal has shoot 'em up and roleplay game things. //
\endgl
\xe

\subsection{Personal life}

\ex
\begingl
\gla  Rey~gu-teraseleter Reyl-pah-thasi rayfa-ta aglad-tay-sa, Siti of Taygers alu-thasi rayfa-sa si~gu-elegibiti si~gu-peke sifothi ifil pothu-pafay tay~gu-rifeyla tayle.//
\glb  AGR~ADJ-transgender Raine-NOM-also write-PST book-ACC-SG,  City of Tigers and-also write-PRS AGR~ADJ-lgbt AGR~ADJ-fake story in 3SG-POS AGR~ADJ-remaining time.//
\glft transgender Raine also wrote a book titled City of Tigers and also writes LGBT-oriented fictional stories in her spare time.//
\endgl
\xe

Thiguka has no construction for "is", so to communicate that Raine is transgender, I had to attach it to Raine's name as an adjective.

\subsection{Awards}

\ex
\begingl
\gla  Asaga-ta Reyl-tay pur olo~gu-bafata thi~gu-olota thil-sa alu-thasi pothu-pafay rifari ifil Selesete risif-ta Gi~gu-arika Giled-pafay Tarifari-elah, pelu-pah-elah rayfa-sa aglad-tay-elah alu pelu-pah-elah fathusi-sa thil-tay-elah ri-gulid ri~gu-kolugeyle rifari ifil fasate thi~gu-olota thil-sa ifil 2019.//
\glb  nominate-PST Raine-ACC for AGR~ADJ-bafta AGR~ADJ-honor thing-SG and 3SG-POS music in Celeste receive-PST AGR~ADJ-America society-POS  musician-PL, person-PL write-PRS book-NOM-PL and person-PL expose-PRS thing-NOM-PL INT-good AGR~ADJ-video game music in year AGR~ADJ-honor thing-SG in 2019//
\glft nominated Raine for a BAFTA award and also her music in Celeste received American Society of Musicians, Authors and Publishers best video game music of the year award in 2019.//
\endgl
\xe

\ex
\begingl
\gla  Pothu-pafay rifari ifil Selesete-pah.thasi risif-ta ri~gu-ri-gulid asa~gu-rifari asaga-sa ifil  thi~gu-kolugeyle thi~gu-olota thil-elah ifil 2018//
\glb  3SG-POS music in Celeste-NOM.also receive-PST AGR~ADJ-INT-good AGR~ADJ-music nomination-SG in  AGR~ADJ-video game AGR~ADJ-honor thing-PL in 2018//
\glft Her music in Celeste also received Best Music nomination in The Game Awards 2018.//
\endgl
\xe

\newpage

\section{English}
Lena Raine (/ˈleɪ.nə/ LAY-nə or /ˈlɛ.nə/ LEN-ə; born February 29, 1984), also known as Lena Chappelle or Kuraine, is an American-Canadian composer, producer, and video game developer.
Raine is best known for her work on the soundtracks of Celeste, Minecraft and Guild Wars 2.
She has composed music for various other video games, including Deltarune and Chicory: A Colorful Tale.

\subsection{Early life}

Raine was born on February 29, 1984 in Seattle, Washington.
Her father is a musician and her mother is a dancer.
She had an early exposure to music due to participation in choir at a young age.
Her father was also a violinist.
Through a Sonic the Hedgehog fan community she was introduced to MIDI arrangement, first recreating versions of songs she knew and then making original music.
She later attended Cornish College of the Arts for a degree in music composition.

\subsection{Career}

Raine is best known for her work on the soundtracks of Celeste and Guild Wars 2.
She worked on Guild Wars 2 at ArenaNet for six years, as a designer and soundtrack composer.
At ArenaNet, she and Maclaine Diemer were in-house composers of the music for the game's 2015 expansion, Guild Wars 2: Heart of Thorns.
She left ArenaNet in 2016, but has continued to occasionally compose songs for its various releases as a freelancer.

In 2018, Raine released the text adventure ESC on itch.io.
Raine was the developer and composer for ESC, with visuals created by Dataerase.
In 2019, she released her debut album, Oneknowing.
She composed music for Minecraft, creating four new pieces of music which were included in the 1.16 "Nether Update" in 2020.
A year later, she returned to Minecraft, composing six new tracks for the 1.18 "Caves \&{} Cliffs: Part II" update, alongside fellow video game composer Kumi Tanioka.
A year after that, she also composed another three new tracks for the 1.19 "The Wild Update", and then about two years later, she composed five new tracks for 1.21 "Tricky Trials".
Raine created the soundtrack for the adventure RPG Chicory: A Colorful Tale, and assisted with the soundtrack for the second chapter of Deltarune, both released in 2021.

On May 28, 2024, Raine announced Anothereal, a game combining elements of shoot 'em up and role-playing video games.

\subsection{Personal life}

Raine is transgender.
She has also written a book titled City Of Tigers, and has begun composing more LGBT-oriented fiction in her spare time.

\subsection{Awards}

Raine was nominated for a BAFTA (British Academy of Film and Television Arts) and won American Society of Composers, Authors and Publishers (ASCAP) Video Game Score of the Year in 2019 for Celeste. Her soundtrack for Celeste was also nominated for Best Score/Music at The Game Awards 2018.
